\includegraphics[width=1.0\textwidth]{SimAUDLogo.png}\\\quad\\A Three-Tier Architecture Visual-Programming Platform for Building-Lifecycle Data Management

### 2020-03-28 paper_LateX/main.tex

The metadata and models are either input by the users through the presentation layer or assigned by the application layer. These data are mainly text. Once passed to the data layer, they are static and stored in the relational databases (Figure \ref{fig:relationDatabase}). As for the building operational data, the time series data comes from servers of different Building Management Systems. BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task. The platform dealt with this by deploying the PI system from OSIsoft \cite{PiSystem}, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
\begin{figure*}
\includegraphics[width=\linewidth]{imgs/uml_relationship.jpeg}
\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}
}
\label{fig:relationDatabase}
\end{figure*}
Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format. For example, if a user wants to see the energy consumption trend of a building, he/she will select the data point and define the time period in VPL canvas. The deep functions in the application layer will get the information and accordingly send the request. The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
\section{Case study} \label{section:casestudy}
In this section, we introduce a case-study to evaluate our platform.

>>>>

The metadata and models are either input by the users through the presentation layer or assigned by the application layer. These data are mainly text. Once passed to the data layer, they are static and stored in the relational databases (Figure \ref{fig:relationDatabase}). As for the building operational data, the time series data comes from servers of different Building Management Systems. BMS in different buildings are various, in terms of data structure, sampling rate, communication protocol, etc., making data querying a troublesome task. The platform dealt with this by deploying the PI system from OSIsoft \cite{PiSystem}, which queries data from different types of servers, such as BACnet (Building Automation and Control networks) and OPC (Open Platform Communications), and stores the compressed data on the local server.\par
\begin{figure*}
\includegraphics[width=\linewidth]{imgs/uml_relationship.jpeg}
\caption{Relational database: A higher resolution image can be downloaded  \href{https://user-images.githubusercontent.com/6969514/72235771-e9e89f80-360e-11ea-9cf7-91c0f521576c.jpeg}{here}
}
\label{fig:relationDatabase}
\end{figure*}
Data exchange between the application layer and the data layer is done through RESTful API and mainly in JSON format. For example, if a user wants to see the energy consumption trend of a building, he/she will select the data point and define the time period in VPL canvas. The deep functions in the application layer will get the information and accordingly send the request. The API will retrieve data from the server and send it back as a JSON file, which will then be plotted in the canvas.
\section{Use cases} \label{section:casestudy}
In this section, we introduce three use-cases to evaluate our platform. The first is a parametric energy simulation of a small office building from ANSI/ASHRAE/IES Standard 90.1 commercial reference buildings
